\documentclass[12pt]{article}
\usepackage{fullpage}
\begin{document}
\noindent {\bf Using Image Diversity Software}

\begin{itemize}
\item {\bf Preparing files}
\begin{enumerate}
	\item Check that all files you want to evaluate have distinct names. Note: We need to systematically name files: 1234item56789abc: 12 designate study, 34 designate subject, item gives the word, 5 identifies repetition of word, 6789 identifies frame number, abc indicates who did the tracing. The tracer (``abc'') could be a person or an automatic tracing, in which case ``abc'' needs to indicate what the training system was...
	\item Move all files into the same folder.
\end{enumerate}

\item {\bf Determining diversity}
\begin{enumerate}
	\item Open terminal.
	\item Type {\it cd} then drag AutoTrace in from the desktop.
	\item At the terminal prompt, type python image\_diversity.py
	\item This should open a window asking for a file. Open the directory, select all relevant files,  click OPEN.
	\item A window opens with the ultrasound images that says ``SELECT ROI'' (Region-Of-Interest). Click on the top left corner and drag the yellow box to get the region you want to be compared.
	\item Wait. There will be signals on the terminal window that things are happening...``calculating average image'' and ``measuring distance from average image'' or some such.
	\item A graph will pop up.
	\item In terminal, it will say ``enter number of images to move''. Use the graph to identify where the diversity index changes dramatically, signaled by a leveling of the curve. This will get the images with the most variation. Hit ENTER.
	\item Terminal tells you what's being copied and where it goes (into a subfolder called ``diverse'' in the directory that the files were in).
	\item Terminal will ask ``Should I also add the 50 least different images?'' n ENtER = ``no'', y ENTER = ``yes''. It's good to include these to have a full range.
	\item ``copythread stopped'' tells you that it is all finished.
\end{enumerate}

\item {\bf The next steps}
\begin{enumerate}
	\item Hand trace the contents of ``diverse''.
	\item Train autotrace on this set.
	\item Use the newly trained autotracer to automatically trace the remaining images.
	\item Inspect the results by eye to see what needs to be fixed; fix those.
	\item For the worst ones, click Bootstrap Add. This will list the correct form of the really bad ones, which can then be added to the training set.
\end{enumerate}
\end{itemize}
\end{document}